\section{Method: Self-Distillation Prompt Augmentation Variants}
\label{sec:method}

We study three prompt-construction variants controlled by four switches in
\texttt{run\_local\_sdpo.sh}:
\texttt{INCLUDE\_ANOTHER\_SOLUTION},
\texttt{INCLUDE\_FAILURE\_SOLUTION},
\texttt{SUMMARIZE\_SOLUTIONS}, and
\texttt{SUMMARY\_FROM\_ALL}.
For each training query, we have a set of rollout responses for the same instance identity $u$,
\begin{equation}
\mathcal{R}(u)=\{r_j\}_{j=1}^{n_u},
\end{equation}
with reward scores $\{y_j\}_{j=1}^{n_u}$. Using threshold $\tau$, we define
\begin{equation}
\mathcal{S}(u)=\{r_j\in\mathcal{R}(u): y_j\ge\tau\},\qquad
\mathcal{F}(u)=\{r_j\in\mathcal{R}(u): y_j<\tau\}.
\end{equation}

Let $x$ be the current prompt, and let $r^{\star}\in\mathcal{S}(u)$ be the primary successful solution
(if it exists). The teacher-augmented context is
\begin{equation}
\tilde{x}=x \oplus \mathcal{C}(u),
\end{equation}
where $\oplus$ denotes text concatenation and $\mathcal{C}(u)$ is variant-specific context.
The policy then optimizes SDPO objective
\begin{equation}
\mathcal{L}_{\text{SDPO}}=(1-\alpha)\,\mathcal{L}_{\text{RL}}+\alpha\,\mathcal{L}_{\text{distill}}(\tilde{x}).
\end{equation}

\subsection{Variant 1: Another Successful Solution}
Configuration:
\texttt{INCLUDE\_ANOTHER\_SOLUTION=True}.

When $|\mathcal{S}(u)|\ge 2$, we select an additional successful response
$r^{+}\in\mathcal{S}(u)\setminus\{r^{\star}\}$ and form
\begin{equation}
\mathcal{C}_1(u)=\texttt{Template}(r^{\star})\oplus\texttt{AnotherTemplate}(r^{+}).
\end{equation}
If only one success is available, $\mathcal{C}_1(u)$ reduces to the primary-solution block.
This variant increases successful-solution diversity while keeping all demonstrations positive.

\subsection{Variant 2: Another Success + Failure-Aware Fallback}
Configuration:
\texttt{INCLUDE\_ANOTHER\_SOLUTION=True},
\texttt{INCLUDE\_FAILURE\_SOLUTION=True}.

This variant keeps Variant 1 behavior when a success exists.
Additionally, when $\mathcal{S}(u)=\varnothing$, we sample a failure
$r^{-}\sim\mathcal{F}(u)$ and provide it as a negative demonstration:
\begin{equation}
\mathcal{C}_2(u)=
\begin{cases}
\mathcal{C}_1(u), & \text{if } \mathcal{S}(u)\neq\varnothing,\\
\texttt{FailureTemplate}(r^{-}), & \text{if } \mathcal{S}(u)=\varnothing.
\end{cases}
\end{equation}
Thus, the model either imitates good trajectories or explicitly avoids known bad trajectories.

\subsection{Variant 3: Summary Distillation from All Responses}
Configuration:
\texttt{INCLUDE\_ANOTHER\_SOLUTION=False},
\texttt{INCLUDE\_FAILURE\_SOLUTION=False},
\texttt{SUMMARIZE\_SOLUTIONS=True},
\texttt{SUMMARY\_FROM\_ALL=True}.

For each candidate response $r_j$, we extract a compact summary
$s_j=\texttt{ExtractSummary}(r_j)$ (or a short fallback excerpt if missing).
Given summary budget $k$, we sample
\begin{equation}
\mathcal{P}_k(u)\subseteq \mathcal{R}(u)\setminus\{r^{\star}\},\qquad |\mathcal{P}_k(u)|\le k,
\end{equation}
and construct
\begin{equation}
\mathcal{C}_3(u)=\texttt{Template}(r^{\star})\oplus
\bigoplus_{r_j\in\mathcal{P}_k(u)}
\texttt{SummaryTemplate}_{\ell_j}(s_j),
\end{equation}
where label $\ell_j\in\{\text{success},\text{failure}\}$ is determined by $y_j\ge\tau$.
Compared with full-solution injection, this variant exposes broader behavioral coverage
(success and failure) with lower context length.

\subsection{Unified View}
All three variants can be written as
\begin{equation}
\mathcal{C}(u)=\texttt{Template}(r^{\star})\oplus
\lambda_{+}\,\mathcal{A}_{+}(u)\oplus
\lambda_{-}\,\mathcal{A}_{-}(u)\oplus
\lambda_{\Sigma}\,\mathcal{A}_{\Sigma}(u),
\end{equation}
where $(\lambda_{+},\lambda_{-},\lambda_{\Sigma})\in\{0,1\}^3$ are switch-controlled gates for
additional success, failure demonstration, and summary blocks, respectively.
The three settings correspond to:
\begin{equation}
\text{V1}:(1,0,0),\qquad
\text{V2}:(1,1,0),\qquad
\text{V3}:(0,0,1;\,\texttt{SUMMARY\_FROM\_ALL}=\texttt{True}).
\end{equation}

In practice, Variant 1 emphasizes positive imitation, Variant 2 improves robustness under sparse success,
and Variant 3 trades token-level detail for higher response diversity via summary-level distillation.
